\thetitle

### 2021-07-01 writing/mutate-benchmarks.tex
Fix grammar and typos
Change table "figures" to tables, with caption at top

\citet{gtnffvf-jfp-2019}'s collection of Typed Racket programs for
systematically measuring the implementation's performance satisfies these
criteria. The benchmark suite consists of fully typed, correct programs, written
by a number of different authors who had maintained and evolved these programs
over time. The programs range widely in size, complexity, purpose,
origin and in programming style. They rely on many Typed Racket features:
occurrence typing~\citep{tf-icfp-2010}, types for mutable and immutable data
structures~\citep{hpst-sfp-2010}, types for first-class classes and
objects~\citep{tsdtf-oopsla-2012}, and types for Racket's numeric
tower~\citep{stathff-padl-12}.  Finally, all of the programs are deterministic,
so any changes in the programs' behavior between runs can be solely attributed
to the actions of the rational programmer.

Figure~\ref{table:benchmark-descriptions} describes the ten benchmark programs that
meet all the criteria, and furthermore come with the largest dependency graphs.
This additional filter reflects that Typed Racket demands type assignments
for entire modules, and so finding errors in benchmarks with small dependency graphs
would almost be trivial for the rational programmer.

>>>>

\citet{gtnffvf-jfp-2019}'s collection of Typed Racket programs for
systematically measuring the implementation's performance satisfies these
criteria. The benchmark suite consists of fully typed, correct programs, written
by a number of different authors who had maintained and evolved these programs
over time. The programs range widely in size, complexity, purpose,
origin, and in programming style. They rely on many Typed Racket features:
occurrence typing~\citep{tf-icfp-2010}, types for mutable and immutable data
structures~\citep{hpst-sfp-2010}, types for first-class classes and
objects~\citep{tsdtf-oopsla-2012}, and types for Racket's numeric
tower~\citep{stathff-padl-12}.  Finally, all of the programs are deterministic,
so any changes in the programs' behavior between runs can be solely attributed
to the actions of the rational programmer.

Table~\ref{table:benchmark-descriptions} describes the ten benchmark programs that
meet all the criteria, and furthermore come with the largest dependency graphs.
This additional filter reflects that Typed Racket demands type assignments
for entire modules, and so finding errors in benchmarks with small dependency graphs
would almost be trivial for the rational programmer.

### 2021-07-01 writing/mutate-interesting.tex
Update changelog
Change table "figures" to tables, with caption at top

The goal of filtering for interesting mutants guided countless iterations of
adding, removing, and refining mutators in figure~\ref{table:mutation-ops}.  For
an illustrative example, Consider a candidate mutator that casts the tests of
conditionals to the {\tt Any} type. Like the example explained at the end of the
preceding subsection, this mutant would suppress occurrence typing. But, it
would not be interesting because an execution would not raise a run-time error;
instead the function would process its input as if nothing had changed. Hence
this candidate mutator is not included in the final set.

>>>>

The goal of filtering for interesting mutants guided countless iterations of
adding, removing, and refining mutators in table~\ref{table:mutation-ops}.  For
an illustrative example, consider a candidate mutator that casts the tests of
conditionals to the {\tt Any} type. Like the example explained at the end of the
preceding subsection, this mutant would suppress occurrence typing. But, it
would not be interesting because an execution would not raise a run-time error;
instead the function would process its input as if nothing had changed. Hence
this candidate mutator is not included in the final set.
